\documentclass{article}
\usepackage{xcolor}
\usepackage{url}

\newcommand{\REPLACE}[1]{{\color{red} #1}}
\newcommand{\REMOVE}[1]{{\color{red} #1}}

\begin{document}

\title{Statements of Individual Contributions}

\author{Martin BAUW, Robin DURAZ, Jiaxin GAO,\\ Hao LIU, and Luca VEYRON-FORRER}
\maketitle
\begin{abstract}
This document details the individual contributions of each group member to the outcome of the group project, benchmarking Adaptive-IBEA with epsilon indicator with the COCO platform. It also includes an anti-plagiarism phrase that needs to be signed by every group member.
\end{abstract}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Individual Contributions to the Group}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
We have all read the article and have understood it on our own before trying to
implement it. We, at the beggining, all tried to implement it with our
understanding of the article, and in the end kept the best (which worked) versions.

\subsection{Martin BAUW}
I tried doing code for almost everything, which was eventually not used. I also
did most of the work for the report, including the description of the algorithm.

\subsection{Robin DURAZ}
I did a basic working version of the full algorithm, taking the code from Hao
LIU. I also ran most of the benchmarking with COCO.

\subsection{Jiaxin GAO}
I tried to understand how COCO works, as the others did, and I did the
comparison with random search and NSGA-II algorithms. 

\subsection{Hao LIU}
I did the code for mating selection and variation, i.e. binary selection,
recombination and mutation on the population. I read articles in order to find
good parameters for those functions.

\subsection{Luca VEYRON-FORRER}
I took the basic version of the algorithm and tried to optimize it, i.e. making
it faster.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Anti-Plagiarism Statement}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
All group work, be it the source code, the documentation, the report, the presentation, or any other contribution have been solely written by the group members or corresponding reused parts have been cited accordingly. We, the group members, confirm herewith as well that we all have read and understood the ``What is plagiarism'' page of \url{http://www.plagiarism.org/plagiarism-101/what-is-plagiarism/}.\\


Robin DURAZ, Jiaxin GAO, Hao LIU, Luca VEYRON-FORRER.

\end{document}
